---
title: "project3"
author: "Adam Gonzalez"
date: "12/18/2019"
output: html_document
---

[Back To Portfolio]()

## ** Gun Violence in todays society and how poverty plays a role

In previous parts of the projects i was putting together more stats and more data, but did not show a modeling of the data that i had gathered so now i will put together a model to show how poverty plays a role in gun violence.

```{r results='hide'}

library('knitr')

if (!file.exists('project2.r')){
  purl('project2.Rmd', output='project2.r')
}

if(!file.exists('project1.r')){
  purl('project.Rmd', output='project1.r')
}

source('project1.r')
source('project2.r')
library(caret)
```

### Gun Violence Data

```{r}

FireArm

```

### Poverty Data

```{r}
poverty <- tibble(state = People$State, abovePoverty = People$Above_Poverty_Rate)

poverty
```

# Adding new poverty data for testing to have more data
```{r}
poverty2.0 <- read_csv("data.csv")
poverty2.0

povertyUpdate <- poverty2.0[order(poverty2.0$State),]
povertyUpdate = povertyUpdate[-9,]
```


```{r}
# new firearm data to include in calculations
FireArm2.0 <- read_csv("data1.csv")
FireArmUpdate <- FireArm2.0[order(FireArm2.0$State),]
```

## ** Plotting together the data of shootings and poverty

```{r}
fireArmPov <- tibble(State = FireArm2.0$State, KillsPerMonth = FireArmUpdate$rate, 
                     povertyRate = povertyUpdate$PovertyRate, population = povertyUpdate$Population)

fireArmPov = filter(fireArmPov, povertyRate < 15)
fireArmPov = filter(fireArmPov, KillsPerMonth < 15)
fireArmPov = filter(fireArmPov, KillsPerMonth != povertyRate)
a = ggplot(fireArmPov, aes(x = State, y = KillsPerMonth)) + geom_col(color = 'blue', width = 1)

a + coord_flip()


b = ggplot(fireArmPov, aes(x = State, y = povertyRate)) + geom_col(color = 'Yellow', width = 1)


b + coord_flip()

```




## setting up the model


```{r}
#Partition into Train(75%) and Test(25%) sets
sample <- createDataPartition(fireArmPov$KillsPerMonth, p=0.75, list=FALSE)
train <- fireArmPov[sample, ]
test <- fireArmPov[-sample, ]

train_model <- lm(KillsPerMonth ~ povertyRate + population, data = train)

summary(train_model)
```
* Now that we did the testing we can see that the p-values are really low
+ we can now tell that the more population there is with a high poverty rate there is lower ammounts of crime
* It was interesting to see since i thought the more poverty and population the more homicides there would be within each state with a higher poverty rate


* Now We can go more in depth and try to look at the predicitions and see if they show anything else more into this talk about if poverty plays a roll
```{r}
predictions <- train_model %>% predict(test)



```
